Parameter Estimation for the CES Model

### 2013-07-19 CES.Rnw
Added additional comments at the end of the document.

The best fit for the UK appears to be $\rho_1 \rightarrow -1$ ($\sigma_1 \rightarrow \infty$, meaning perfect subsitutibility between $k$ and $l$). It is unclear why there is a sudden dropoff in $-SSE$ at larger values of $\rho$.

>>>>

The best fit for the UK appears to be $\rho_1 \rightarrow -1$ 
($\sigma_1 \rightarrow \infty$, 
meaning perfect subsitutibility between $k$ and $l$). 
The sudden dropoff in $-SSE$ at larger values of $\rho$ 
should be investigated.

Figure~\ref{fig:UKQ-grid-fine} makes it clear 
that it will be difficult to achieve convergence 
for the UK CES model with $q$ unless the cause of the steep
dropoff can be understood.
